### 2014-01-10 Docs/architecture/architecture.tex
Added to the documentation an explanation of each box's meaning in a fab.

A \fab\ is a ``Fortran Array Box''.  It contains the state data in a
multidimensional array and several \boxtype-types to describe where in
the global index-space it lives.  
Note that all state data is stored in a four-dimensional array,
{\tt (nx,ny,nz,nc)} in size, regardless of the dimensionality of the
problem.  Here {\tt nc} is the number of components, for instance
representing different fluid variables.  For 2D problems, {\tt nz=1}.

>>>>

A \fab\ is a ``Fortran Array Box''.  It contains the state data in a
multidimensional array and several \boxtype-types to describe where in
the global index-space it lives:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  type fab
     ...
     type(box) :: bx
     type(box) :: pbx
     type(box) :: ibx
  end type fab
\end{lstlisting}
{\tt bx} represents the box in the global index-space over which the 
\fab\ is defined, {\tt pbx} represents the ``physical'' box in the sense
that it includes {\tt bx} plus ghost cells, and {\tt ibx} is the same as {\tt bx} unless 
the \fab\ is nodal.  As can be seen in Figure~\ref{fig:dataloc},
for the same grid nodal data requires one more array element than 
cell-centered data.  To address this {\tt ibx} is made by growing
{\tt bx} by one element along all nodal dimensions.

It's important to note that all state data is stored in a four-dimensional array
{\em regardless of the problem's dimensionality}.  The array is 
{\tt (nx,ny,nz,nc)} in size, where {\tt nc} is the number of components, for instance
representing different fluid variables, and {\tt (nx,ny,nz)} are the number of cells
in each respective spatial dimension.  For 2D problems, {\tt nz=1}.
